Discovering Focused Microgenre Communities

### 2023-08-03 main.tex
Updates from Overleaf

\begin{figure}[ht!]
    \centering    
    \includegraphics[width=1.3\textwidth]{Tabs/reg-tab-metal.png}
    \caption{}
    \label{tab:reg-metal}
\end{figure}

To examine these questions, I partitioned the Heavy-Metal branch of the dendrogram, at a height that resulted in four microgenre variations. To explore the issue of audience segmentation, I specify a linear probability regression model with five outcomes: First, a binary variable indicating that a person chose (liked and listened to) the standard macrogenre label (Heavy Metal), and then four models with the microgenre variations as the outcome (Heavy Metal one through four). The results are shown in Table~\ref{tab:reg-metal}. The main predictors are the respondent's education, an indicator variable for whether at least one of the respondent's parents has a college degree, respondent's age, racial identification (in five categories), and gender identification (in two categories). Because the age effect is specified using a squared polynomial, it can be hard to interpret its substantive significance. To help with this, I show the predicted probabilities obtained for the model at different values of age for the four different microgenres in Figure~\ref{fig:age-metal}.

@@

Not so fast. The results are different when looking at the predictors of the microgenre variation choices. Indeed, the predictors of choosing the first microgenre variation, shown in the second column of the table, are consistent with Tampubolon's story. For this microgenre, there is a flat education gradient ($p = 0.54$), and importantly, it is more likely to be consumed by people whose parents have a college degree ($p < 0.05$), indicating a link to cultural capital in the home environment. This microgenre is tilted towards younger audiences, as only the linear negative age term is statistically significant (see Figure~\ref{fig:age-metal}) and is also neutral with respect to race and gender. This version of Metal appeals mainly to young middle-class respondents and does not repel women or non-white audiences, a stark difference from what we would have concluded from observing the macrogenre label effects.

@@

\begin{figure}[ht!]
    \centering    
    \includegraphics[width=1.3\textwidth]{Tabs/reg-tab-latin.png}
    \caption{}
    \label{tab:reg-metal}
\end{figure}

>>>>

\begin{figure}[ht!]
    \centering    
    \includegraphics[width=1.5\textwidth]{Tabs/reg-tab-metal.png}
    \caption{}
    \label{tab:reg-metal}
\end{figure}

To examine these questions, I partitioned the Heavy-Metal branch of the dendrogram, at a height that resulted in four microgenre variations. To explore the issue of audience segmentation, I specify a linear probability regression model with five outcomes: First, a binary variable indicating that a person chose (liked and listened to) the standard macrogenre label (Heavy Metal), and then four models with the microgenre variations as the outcome (Heavy Metal one through four). The results are shown in Table~\ref{tab:reg-metal}. The main predictors are the respondent's education, an indicator variable for whether at least one of the respondent's parents has a college degree, the respondent's age, racial identification (in five categories), and gender identification (in two categories). Because the age effect is specified using a squared polynomial, it can be hard to interpret its substantive significance. To help with this, I show the predicted probabilities obtained for the model at different age values for the four different microgenres in Figure~\ref{fig:age-metal}.

@@

Not so fast. The results differ when looking at the predictors of the microgenre variation choices. Indeed, the predictors of choosing the first microgenre variation, shown in the second column of the table, are consistent with Tampubolon's story. For this microgenre, there is a flat education gradient ($p = 0.54$), and importantly, it is more likely to be consumed by people whose parents have a college degree ($p < 0.05$), indicating a link to cultural capital in the home environment. This microgenre is tilted towards younger audiences, as only the linear negative age term is statistically significant (see Figure~\ref{fig:age-metal}) and is also neutral with respect to race and gender. This version of Metal appeals mainly to young middle-class respondents and does not repel women or non-white audiences, a stark difference from what we would have concluded from observing the macrogenre label effects.

@@

``Taste in salsa music shows a strong internal, hierarchical order between ‘artistic’ versus ‘popular’ styles that is not only acknowledged and defined as such by experts and professionals within the field, but also structures the taste patterns of different social classes'' \citeyearpar[][62]{Bachmayer2014-pk}

\begin{figure}[ht!]
    \centering    
    \includegraphics[width=1.5\textwidth]{Tabs/reg-tab-latin.png}
    \caption{}
    \label{tab:reg-metal}
\end{figure}
